Compiling refinement types to dependent types

### 2020-07-19 tex/paper.tex
Add context well-formedness rules
Unite typing and subtyping rules figures
Refer the core/surface syntax/typing figures

@@

@@

\begin{figure}[ht]
  \footnotesize
  \drules[TWF]{$\nonterm G \vdash \nonterm{ts}$}{type well-formedness}{TrueRef,Base,Conj,Arr}
  \drules[T]{$\nonterm G \vdash \nonterm{es} : \nonterm{ts}$}{term typing}{Unit,Var,Abs,App,Case,Con,Sub}
  \caption{Surface language typing}
  \label{fig:surface_typing}
\end{figure}

\begin{figure}[ht]
  \footnotesize
  \drules[ST]{$\nonterm G \vdash \nonterm{ts}_1 <: \nonterm{ts}_2$}{subtyping}{Base,Arr}
  \caption{Surface language subtyping}
  \label{fig:surface_subtyping}
\end{figure}

@@

>>>>

\newcommand{\figref}[1]{Figure \ref{fig:#1}}

@@

The syntax of the surface language is presented in \figref{surface_syntax}.

The typing rules for the surface language are laid out in \figref{surface_typing}.
For the type well-formedness and term typing rules
we also assume each of them has a premise $\nonterm G \text{ ok}$
stating that the context is well-formed.

@@

\begin{figure}[ht]
  \footnotesize
  \drules[TCTX]{$\nonterm G \text{ ok}$}{context well-formedness}{Empty,Bind}
  \drules[TWF]{$\nonterm G \vdash \nonterm{ts}$}{type well-formedness}{TrueRef,Base,Conj,Arr}
  \drules[T]{$\nonterm G \vdash \nonterm{es} : \nonterm{ts}$}{term typing}{Unit,Var,Abs,App,Case,Con,Sub}
  \drules[ST]{$\nonterm G \vdash \nonterm{ts}_1 <: \nonterm{ts}_2$}{subtyping}{Base,Arr}
  \caption{Surface language typing}
  \label{fig:surface_typing}
\end{figure}

@@

The syntax of the core language is presented in \figref{core_syntax},
and the typing rules are defined in \figref{core_typing}.
